\LARGE \bf TODO Name this thing

### 2012-02-17 papers/itsc_2012/root.tex
some minor changes to abstract

\begin{abstract}
Write this.
\end{abstract}

@@

Autonomous vehicles have seen tremendous progress in recent years. In 2004, no autonomous vehicle was able to complete the course set out in the first DARPA Challenge. By 2007, 5 vehicles finished the course of 130 miles in urban environments. By 2011, autonomous vehicles projects have now touched 160,000 miles and an autonomous car drove for 13,000 miles in Europe. Autonomous cars are here to stay, and this changes how traffic is dealt with in the forseeable future. The infrastructure will change to support autonomous vehicles, but it is hard to say more about our traffic demands. Will we be able to gain more roads in the future. Do we have the space to expand and will autonomous vehicles be able to reach your doorstep.

>>>>

\begin{abstract}
Autonomous vehicle technology have seen great advancements in recent years and are closer to being commercially viable. Driverless cars provide opportunities for optimizing traffic across cities in ways not possible before. This paper explores such scenarios and introduces a new traffic micro-simulator named AORTA. AORTA emphasizes research using scale simulations generated from OpenStreetMap data. This paper presents parsing map through the simulator and using the AORTA simulator. It concludes with some preliminary results that demonstrate the power of this simulator.   
\end{abstract}

@@

Autonomous vehicles have seen tremendous progress in recent years. The DARPA Challenge in 2004 saw the farthese distance being traversed autonomously as In 2004, no autonomous vehicle was able to complete the course set out in the first DARPA Challenge. By 2007, 5 vehicles finished the course of 130 miles in urban environments. By 2011, autonomous vehicles projects have now touched 160,000 miles and an autonomous car drove for 13,000 miles in Europe. Autonomous cars are here to stay, and this changes how traffic is dealt with in the forseeable future. The infrastructure will change to support autonomous vehicles, but it is hard to say more about our traffic demands. Will we be able to gain more roads in the future. Do we have the space to expand and will autonomous vehicles be able to reach your doorstep.
